%!TEX root = ../dissertation.tex
% the acknowledgments section

\paragraph{}
First, I want to thank you, the reader, for reading this thesis and acknowledgments now. 
\paragraph{}
I have many people and organizations to thank. Without them I would not have finished this thesis or my Ph.D. in physics. Thanks to:
\begin{itemize}
	\item \newthought{Melissa Franklin}, the best adviser ever. Every time I get stuck, Melissa is always there to guide me and show me the light at the end of the tunnel. She always pushes me to understand the details I ignore and think about every result I get. I learned how to read, write, plot, think and talk from her. I also learned how to teach physics from working with her in teaching Physical Science 12. Her encouragement, advice, and commentary have always been inspirational and keep me moving ahead.
	\item \newthought{Masahiro Morii}, for being on my committee, and offering physics guidance and discussions. You have always been insightful.
	\item \newthought{Howard Georgi}, for being on my committee, and having me teach Physics 16 with you. It is always nice to talk about physics with you.
	\item \newthought{Jo\~{a}o Guimar\~{a}es da Costa}, for your enthusiasm about physics. I have always enjoyed talking about LHC physics with you. You got me interested in di-Higgs and have always been very supportive.
	\item \newthought{Paolo Giromini}. You taught me how to work on Micromegas, always have great comments on physics and scolding, and ask for the White Rabbits.
	\item \newthought{John Huth}, for all your support and great stories.
	%%%%%%%%%%%%%%%
	\item \newthought{The Chinese, the U.S., the French and the Switzerland governments}. Without their generous support, I couldn't have studied and lived in these different countries.
	\item \newthought{CERN}. CERN is a unique and special place with the streets named after physicists. Without the support from the IT department, I could not log into Lxplus, check the Twikis, or finish my work. CERN user's office also made traveling to Europe a much nicer and easier experience for me.
	\item \newthought{The LHC}. Without a fully functional accelerator, there would have been no data for me to study. The LHC has performed outstandingly since 2015, and all the data in this thesis is produced from it. 
	\item \newthought{Everyone in the ATLAS collaboration}. They have supported this remarkable program and have contributed enormously to my thesis. Without the excellent work on detector design, commissioning, operational work, reconstruction, data processing, performance studies and recommendations, software support, computing support, and analysis discussions and guidance, I could not have completed this thesis. I sincerely thank all ATLAS members for their work.
	%%%%%%%%%%%%%%%
	\item \newthought{ATLAS Muon experts}. Thanks to Christoph Amelung for his support. Thanks to Ioannis Nomidis, for his guidance on Athena and Muon Monitoring Software. Thanks to Philipp Fleischmann and TieSheng Dai for teaching me about the ATLAS control room and Muon detectors, and for bringing me down to the detector. Thanks to Niels van Eldik, for his guidance on Hough Transform, segment reconstruction and seeding. Thanks to Jochen Meyer, for his patience, help, and discussions on Muon reconstruction and software writing.
	%%%%%%%%%%%%%%%
	\item \newthought{ATLAS di-Higgs to $4b$ group}. Thanks to Mel Shochet for his support. Thanks to Michael Kagan, for his guidance, patience, and pushing. Thanks to John Allison, for always doing great and ambitious work. Thanks to David Wardrope, for his help on statistical analysis. Thanks to Jana Schaarschmidt, for finishing the paper. Thanks to Stephane Willocq for asking great questions. Thanks to Qi Zeng, for the his help and useful discussions. Thanks to Patrick Bryant, for doing the equally hard work and finishing the resolved di-Higgs analysis. Without them, I would not have completed the di-Higgs analysis.
	%%%%%%%%%%%%%%%
	\item \newthought{Harvard ATLAS group post-docs}. I want to thank Alex Tuna, for his patience, help, and kind support in Muon work and di-Higgs analysis. He always gives good advice on talks and on ZERO. I want to thank Pierluigi Catastini, for working on early di-Higgs studies with me in summer 2014; Hugh Skottowe, for his help on Micromegas and C code; David Lopez Mateos, for his discussions on physics and asking for plots and espressos; Chris Rogan, for his passion and great insights in analysis; Valerio Ippolito, for following up on questions; Geraldine Conti, Stefano Zambito and Larry Lee, for their discussions and help.
	%%%%%%%%%%%%%%%
	\item \newthought{Stephen Chan}, for his great company as a roommate and awesome-o discussions on ATLAS and physics. He edited this thesis more than his own.
	%%%%%%%%%%%%%%%
	\item \newthought{Harvard ATLAS graduate students}. Thanks to Tomo Lazovich for being wonderful elder graduate students and work with me on the analysis. Thanks to Emma Tolley for her mulled wine and lemon pudding. Thanks to Karri Di Petrillo for all the adventures and great conversations. Thanks to Ann Wang for being so helpful and not mad at my mocking. I want to also thank Laura Jeanty, Giovanni Zevi Della Porta, Kevin Mercurio, William Spearman, Andy Yen, Brian Clark for their discussions. Thanks to Siyuan Sun for his laughs, Jennifer Roloff and Julia Gonski for the nice conversations. And Gareth Kafka, even though you worked on neutrinos.
	%%%%%%%%%%%%%%%
	\item \newthought{Harvard ATLAS undergraduate students}. I want to thank Michael Albergo, Gray Putnam, and Jonah Philion, the three undergraduates I have worked with over the past summers. Also thanks to the undergraduate students in my Physics 16, 125 and Physical Science 12 sections.
	\item \newthought{Anna Klales and Lakshminarayanan Mahadevan}. I had wonderful teaching experiences with you in Physical Science 12 and Physics 125.
	\item \newthought{Harvard physics staff}. I want to thank Lisa Cacciabaudo, Carol Davis, Jacob Barandes, Korin Watras, and Angela Allen for being extremely helpful and supportive.
	%%%%%%%%%%%%%%%
	\item \newthought{Caltech and my undergraduate advisers}. Thomas Tombrello, thanks for teaching me how to do research. Stephen Padin, thanks for teaching me how to do an experiment in a lab. Gil Refael, thanks for being a great a friend and great discussions. Harvey Newman, thanks for teaching me EM and special relativity, and all the help and support on my research. And Maria Spiropulu, thanks for show me how exciting particle physics is. Coach Clinton Dodd, for teaching me how to swim and how to start learning. I also want to thank Yi Chen, who taught me a lot when I was a junior on CMS.
	%%%%%%%%%%%%%%%
	\item \newthought{Ludwig van Beethoven and Gustav Mahler}. Thanks to their great music, which accompanied me through many long nights.
	\item \newthought{Boston Symphony Orchestra}, for its affordable tickets and great performances.
	%%%%%%%%%%%%%%%
	\item \newthought{Chi Feng, Helena Zhang, Peter Koch, Jennifer Hu}. Thanks for being my wonderful friends from Caltech.
	\item \newthought{Xinyu Yang, Chi Zhang, Rundong Ning, Boqi Zhu, Yizhou Jin}. Thanks for being my friends for the past decade since we attended Beijing High School Four.
	\item \newthought{Weidong Tong}, my father. You have always been the smartest person I know.
	\item \newthought{Liping Sun}, my mother. You have always been the wisest person I know.
	\item \newthought{Xuyang Ma}. I didn't find a new particle, but I found you.
\end{itemize}


